### 2016-07-18 version0.0/paper1.tex
Completed paper1 and 3

\chapter[Star formation laws in M31]{Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}
\label{ch: paper1}

\section{Introduction}
\label{sec: intro_sfl}
%P1: Star formation laws and why they are important (introducing K-S law and E-S law)

@@

\begin{table*}
\centering
\caption{Data used in this study.}
\label{table:data}
\begin{tabular}{@{}lcccc}
\hline\hline
Wavelength & FWHM & Coverage area &Telescope
& Ref. \\
\hline
%500 \um & 36\arcsec & $Herschel$ & \citet{Fritz12} \\
%250 \um & 18\arcsec.2 & $Herschel$ & \citet{Fritz12} \\
1550~\AA & 4\arcsec.5 & 5\degr $\times$ 5\degr &GALEX & \citet{Martin05}\\  
2250~\AA & 6\arcsec & 5\degr $\times$ 5\degr &GALEX & \citet{Martin05}\\
6570~\AA  & 1\arcsec & 2\degr.2 $\times$ 0\degr.6 &KPNO& \citet{Massey07}\\
3.6~\um & 1\arcsec.7 & 3\degr.7 $\times$ 1\degr.6 &\Spitzer & \citet{Barmby06} \\ 
8~\um & 1\arcsec.9 & 3\degr $\times$ 1\degr &\Spitzer & \citet{Barmby06} \\ 
24~\um & 6\arcsec & 3\degr $\times$ 1\degr &\Spitzer & \citet{Gordon06} \\ 
70~\um & 18\arcsec & 3\degr $\times$ 1\degr &\Spitzer & \citet{Gordon06} \\
160~\um & 12\arcsec & 5\degr.5 $\times$ 2\degr.5 &\Herschel & \citet{Fritz12} \\
350~\um & 24\arcsec.9 & 3\degr $\times$ 1\degr &\Herschel & \citet{Groves12} \\
2.6~mm & 23\arcsec & 2\degr $\times$ 0\degr.5 &IRAM 30-m & \citet{Nieten06}\\
21~cm & 60\arcsec $\times$ 90\arcsec & 5\degr.2 $\times$ 1\degr.5 &DRAO & \citet{Chemin09}\\
\hline
\end{tabular}
\end{table*}

@@

%\subsection{Radio Emission}
Gas densities in galaxies are derived from observations at millimetre and centimetre radio wavelengths.
Emission from the $^{12}$CO (J:$1\rightarrow0$) line observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of M31's interstellar medium. This map covers a 2\degr $\times$ 0\degr.5 region with an angular resolution of 23\arcsec and has the smallest coverage of the galaxy among the maps we used in this paper. In this study, we also used a 21-cm emission map of the atomic gas (H\,{\textsc i}) in M31 from \citet{Chemin09}. This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a 5\degr.1 $\times$ 1\degr.5 region with an angular resolution of 60\arcsec $\times$ 90\arcsec.

\section{Measuring the components of Star Formation Laws}
Before studying the star formation laws, we need to calculate the components of these laws. We used different data and calibrations to produce the SFR maps, the stellar mass surface density and the gas mass surface density. In this section we describe how we measured each ingredient using available data, and calibrations. To use these calibrations, we assumed the M31 distance to be 0.78~Mpc~\citep{McConnachie05}. The ``total'' values recorded in this paper are integrated out to a distance of~25~kpc from the centre of the galaxy along the major axis.

@@

%----------------------------------------------------------------------------------------
%STAR FORMATION RATE
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\subsection{Star Formation Rate}
\label{sec:sfr}
\subsubsection{FUV plus 24~$\mu$m Star Formation Rate}

Our first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \citet{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}. The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction. On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $<10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the~\citet{Kroupa03} IMF as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{\mathrm obs}+3.89L(24\mu m)],
\end{equation}
\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\mathrm obs}$ are in erg~s$^{-1}$. L(FUV)$_{\mathrm obs}$ is the luminosity of the galaxy in the FUV. The subscript "obs" indicates that the FUV emission is not corrected for extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \citet{Leroy08}. We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission. This process results in masking about 3 per cent of the pixels within a 25~kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR. 
Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map. We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$. The reported uncertainty for the total SFR only considers the values we measured and does not include uncertainties related to the masked pixels.

\begin{figure}
    \centering
       \includegraphics[width=\textwidth]{../image_paper1/sfr_fir.eps}
    \caption {SFR map calculated from total infrared emission (see Section~\ref{sec:sfr_fir}). The SFR map here has an angular resolution of 18\arcsec and pixel size of 9.85\arcsec, the same as the MIPS 70 $\mu$m map.}
    \label{fig:sfrs}
\end{figure}

@@

%----------------------------------------------------------------------------------------
%ISM
%----------------------------------------------------------------------------------------

\subsection{Gas Surface Density}
\label{sec:ISM}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/star.eps}
\caption{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
\label{fig:stellarmass}
\end{figure}

Emission in near-infrared bands, such as 3.6~$\mu$m, 4.5~\um and $K$-band, is almost insensitive to emission from young stellar populations, dust absorption and emission, which makes these bands good tracers of the mass of older stellar populations \citep[e.g.][]{Elmgreen84, Eskew12, Zhu10}.We calculated the stellar mass within M31 using a calibration of the 3.6 \um flux by \citet{Eskew12}. They used data from the Large Magellanic Cloud and introduced an empirical relation between stellar mass and flux:
\begin{equation}
\label{equ:eskew}
M _{\star}= 10^{5.97} F_{3.6}\left(\frac{D}{0.05}\right)^2,
\end{equation}
\noindent where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is the 3.6~\um flux in Jy, and $D$ is the distance to the galaxy in Mpc. This calibration is based on the \citet{Salpeter55} IMF. Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration to the Kroupa IMF (see Section~\ref{sec: imf}). We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ:eskew} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission. We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $F_{3.6 \mu m}$ and $F_{4.5 \mu m}$, though this was not mentioned in the aforementioned paper. 
Fig.~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image. Using the coverage map of the IRAC 3.6~\um data, we used only pixels with coverage of more than 2 images per sky position, and replaced the rest with zero M$_{\odot}$. The replaced pixels include less than 8 per cent of the data;  since these pixels are mainly  in regions with low surface brightness, their effect on the final total mass is less than 1 per cent.
Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6 per cent. This result is in fairly good agreement with the results of \citet{Tamm12}. They calculate the stellar mass of M31 to be $(10-15) \times 10^{10}$M$_{\odot}$, 56 per cent of which is in the disk with the rest in the bulge of the galaxy. In their recent work on the stellar mass of M31, \cite{Viaene14} measured the total stellar mass using the integrated fluxes to be $5.49 \times 10^{10}$M$_{\odot}$, which is in good agreement with our result.

@@

%----------------------------------------------------------------------------------------
%SFR LAWS
%----------------------------------------------------------------------------------------
\section{Scaling the star formation rate}
\subsection{Fitting method}
\label{sec:fitting}

%=164mm, height=218mm
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/ks_all_density.pdf}
\caption{Results from fitting the Kennicutt-Schmidt law to data from the whole galaxy using the pixel-by-pixel method. The colour represents the density of the pixels, increasing from blue to red. The number of points among the three columns is different due to the different angular resolution of the H\,{\textsc i} and H$_2$ maps. Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc (for maps with resolution of 23\arcsec) while each point for which the surface density of H\,{\textsc i} or total gas mass is a tracer represents a region of size $\sim$155~pc (for maps with resolution of 60\arcsec $\times$ 90\arcsec). Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
\label{fig:ks_all}
\end{figure}

@@

We also tested each law on three different regions which were chosen in the same manner as explained in Section~\ref{sec:metal}. Applying the SFR laws in these regions provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws such as metallicity, gas mass, stellar mass gradients and changing the ratio of H$_2$ to H\,{\textsc i}.

\subsection{Star formation laws}
\label{sec: sfl}

@@

\includegraphics[width=\textwidth]{../image_paper1/Results_all_3_regs_after_err_co.pdf}
\caption{Same as Fig.~\ref{fig:ks_all}, but in this figure we separated pixels from different regions in the galaxy by their colours. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}%%
\label{fig:ks,regs}
\end{figure}

@@

\begin{figure}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_tot2_f.png}
        \caption{The result from fitting the extended Schmidt law on the surface density of SFR(FUV + 24~$\mu$m), the surface density of total gas and the surface density of stellar mass ($z$-axis) from the whole galaxy. Solid line shows the best fit (the mean value of the range reported in Table~\ref{table:res}) from a pixel-by-pixel method. Equivalent plots for the other SFR and gas tracers are in Fig.s~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} in the appendix.}
        \label{fig:es,all,fuv,tot}
    \end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/color_3d_fuv_tot.png}
\caption{Fitting result for SFR(FUV + 24~$\mu$m) vs total gas. Same as Fig.~\ref{fig:es,all,fuv,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}
\label{fig:es,regs,fuv,tot}
\end{figure}

@@

\subsection{The K-S law in M31}

@@

\subsection{The extended Schmidt law in M31}
\label{sec:es_res}
The extended Schmidt law has been a recently proposed law \citep{Shi11}, which shows a tight correlation between the SFR and the total gas surface density and the surface density of the stellar mass. Our results from fitting the whole galaxy shows a sub-linear relation between \sigmasfr and \sigmastar.
Using only atomic gas, $\beta$ is in good agreement with the original suggestion of the extended Schmidt law, $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$. However, $\beta$ is much smaller in other two gas tracers. Using total gas mass, we find $\eqnprime$ to be very close to $\beta$. This relation suggests that, although increasing the total gas causes a decrease to the SFE, the existing stars will increase the SFE.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/metal_with_errors.png}
    \caption{Left: the SFR(FUV + 24~$\mu$m) surface density versus gas/dust mass ratio surface density and right: Stellar mass versus gas/dust mass ratio surface density  shows the stellar mass. Each point shows a region with size of $\sim$750~pc. Typical uncertainties of the x-axes within 18~kpc are shown in upper right side of the plots. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}
    \label{fig:metal}
\end{figure}

>>>>

\chapter[Star Formation Laws in M31]{Star Formation Laws in the Andromeda Galaxy: Gas, Stars, Metals and the Surface Density of Star Formation}
\label{ch: paper1}
\section{Introduction}
\label{sec: intro_sfl}
%P1: Star formation laws and why they are important (introducing K-S law and E-S law)

@@

\begin{table}
\centering
\caption{Data used in this study.}
\label{table:data}
\begin{tabular}{@{}lcccc}
\hline\hline
Wavelength & FWHM & Coverage area &Telescope
& Ref. \\
\hline
%500 \um & 36\arcsec & $Herschel$ & \citet{Fritz12} \\
%250 \um & 18\arcsec.2 & $Herschel$ & \citet{Fritz12} \\
1550~\AA & 4\arcsec.5 & 5\degr $\times$ 5\degr &GALEX & \citet{Martin05}\\  
2250~\AA & 6\arcsec & 5\degr $\times$ 5\degr &GALEX & \citet{Martin05}\\
6570~\AA  & 1\arcsec & 2\degr.2 $\times$ 0\degr.6 &KPNO& \citet{Massey07}\\
3.6~\um & 1\arcsec.7 & 3\degr.7 $\times$ 1\degr.6 &\Spitzer & \citet{Barmby06} \\ 
8~\um & 1\arcsec.9 & 3\degr $\times$ 1\degr &\Spitzer & \citet{Barmby06} \\ 
24~\um & 6\arcsec & 3\degr $\times$ 1\degr &\Spitzer & \citet{Gordon06} \\ 
70~\um & 18\arcsec & 3\degr $\times$ 1\degr &\Spitzer & \citet{Gordon06} \\
160~\um & 12\arcsec & 5\degr.5 $\times$ 2\degr.5 &\Herschel & \citet{Fritz12} \\
350~\um & 24\arcsec.9 & 3\degr $\times$ 1\degr &\Herschel & \citet{Groves12} \\
2.6~mm & 23\arcsec & 2\degr $\times$ 0\degr.5 &IRAM 30-m & \citet{Nieten06}\\
21~cm & 60\arcsec $\times$ 90\arcsec & 5\degr.2 $\times$ 1\degr.5 &DRAO & \citet{Chemin09}\\
\hline
\end{tabular}
\end{table}

@@

%\subsection{Radio Emission}
Gas densities in galaxies are derived from observations at millimetre and centimetre radio wavelengths.
Emission from the $^{12}$CO (J:$1\rightarrow0$) line observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of M31's interstellar medium. This map covers a 2\degr $\times$ 0\degr.5 region with an angular resolution of 23\arcsec and has the smallest coverage of the galaxy among the maps we used in this paper. In this study, we also used a 21-cm emission map of the atomic gas (H\,{\textsc i}) in M31 from \citet{Chemin09}. This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a 5\degr.1 $\times$ 1\degr.5 region with an angular resolution of 60\arcsec $\times$ 90\arcsec.
\section{Measuring the Components of Star Formation Laws}
Before studying the star formation laws, we need to calculate the components of these laws. We used different data and calibrations to produce the SFR maps, the stellar mass surface density and the gas mass surface density. In this section we describe how we measured each ingredient using available data, and calibrations. To use these calibrations, we assumed the M31 distance to be 0.78~Mpc~\citep{McConnachie05}. The ``total'' values recorded in this paper are integrated out to a distance of~25~kpc from the centre of the galaxy along the major axis.

@@

%----------------------------------------------------------------------------------------
%STAR FORMATION RATE
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\subsection{Star Formation Rate}
\label{sec:sfr}
\subsubsection{FUV Plus 24~$\mu$m Star Formation Rate}

Our first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \citet{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}. The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction. On the other hand, 24~$\mu$m emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $<10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the~\citet{Kroupa03} IMF as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{\mathrm obs}+3.89L(24\mu m)],
\end{equation}
\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\mathrm obs}$ are in erg~s$^{-1}$. L(FUV)$_{\mathrm obs}$ is the luminosity of the galaxy in the FUV. The subscript "obs" indicates that the FUV emission is not corrected for extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \citet{Leroy08}. We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission. This process results in masking about 3 per cent of the pixels within a 25~kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR. 
Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map. We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$. The reported uncertainty for the total SFR only considers the values we measured and does not include uncertainties related to the masked pixels.

\begin{figure}
    \centering
       \includegraphics[width=\textwidth]{../image_paper1/sfr_fir.eps}
    \caption[SFR map calculated from total infrared emission ]{SFR map calculated from total infrared emission (see Section~\ref{sec:sfr_fir}). The SFR map here has an angular resolution of 18\arcsec and pixel size of 9.85\arcsec, the same as the MIPS 70 $\mu$m map.}
    \label{fig:sfrs}
\end{figure}

@@

%----------------------------------------------------------------------------------------
%ISM
%----------------------------------------------------------------------------------------
\subsection{Gas Surface Density}
\label{sec:ISM}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/star.eps}
\caption[Stellar mass surface density map produced using IRAC 3.6~$\mu$m data]{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
\label{fig:stellarmass}
\end{figure}

Emission in near-infrared bands, such as 3.6~$\mu$m, 4.5~\um and $K$-band, is almost insensitive to emission from young stellar populations, dust absorption and emission, which makes these bands good tracers of the mass of older stellar populations \citep[e.g.][]{Elmgreen84, Eskew12, Zhu10}.We calculated the stellar mass within M31 using a calibration of the 3.6 \um flux by \citet{Eskew12}. They used data from the Large Magellanic Cloud and introduced an empirical relation between stellar mass and flux:
\begin{equation}
\label{equ:eskew}
M _{\star}= 10^{5.97} F_{3.6}\left(\frac{D}{0.05}\right)^2,
\end{equation}
\noindent where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is the 3.6~\um flux in Jy, and $D$ is the distance to the galaxy in Mpc. This calibration is based on the \citet{Salpeter55} IMF. Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration to the Kroupa IMF (see Section~\ref{sec: imf}). We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ:eskew} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission. We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $\mathrm{F}_{3.6 \mu \mathrm{m}}$ and $\mathrm{F}_{4.5 \mu \mathrm{m}}$, though this was not mentioned in the aforementioned paper. 
Fig.~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image. Using the coverage map of the IRAC 3.6~\um data, we used only pixels with coverage of more than 2 images per sky position, and replaced the rest with zero M$_{\odot}$. The replaced pixels include less than 8 per cent of the data;  since these pixels are mainly  in regions with low surface brightness, their effect on the final total mass is less than 1 per cent.
Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6 per cent. This result is in fairly good agreement with the results of \citet{Tamm12}. They calculate the stellar mass of M31 to be $(10-15) \times 10^{10}$M$_{\odot}$, 56 per cent of which is in the disk with the rest in the bulge of the galaxy. In their recent work on the stellar mass of M31, \cite{Viaene14} measured the total stellar mass using the integrated fluxes to be $5.49 \times 10^{10}$M$_{\odot}$, which is in good agreement with our result.

@@

%----------------------------------------------------------------------------------------
%SFR LAWS
%----------------------------------------------------------------------------------------
\section{Scaling the Star Formation Rate}
\subsection{Fitting Method}
\label{sec:fitting}

%=164mm, height=218mm
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/ks_all_density.pdf}
\caption[Results from fitting the Kennicutt-Schmidt law to M31 data from the whole galaxy]{Results from fitting the Kennicutt-Schmidt law to data from the whole galaxy using the pixel-by-pixel method. The colour represents the density of the pixels, increasing from blue to red. The number of points among the three columns is different due to the different angular resolution of the H\,{\textsc i} and H$_2$ maps. Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc (for maps with resolution of 23\arcsec) while each point for which the surface density of H\,{\textsc i} or total gas mass is a tracer represents a region of size $\sim$155~pc (for maps with resolution of 60\arcsec $\times$ 90\arcsec). Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
\label{fig:ks_all}
\end{figure}

@@

We also tested each law on three different regions which were chosen in the same manner as explained in Section~\ref{sec:metal}. Applying the SFR laws in these regions provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws such as metallicity, gas mass, stellar mass gradients and changing the ratio of H$_2$ to H\,{\textsc i}. 
\subsection{Star Formation Laws}
\label{sec: sfl}

@@

\includegraphics[width=\textwidth]{../image_paper1/Results_all_3_regs_after_err_co.pdf}
\caption[Results from fitting the Kennicutt-Schmidt law to data from three regions in M31]{Same as Fig.~\ref{fig:ks_all}, but in this figure we separated pixels from different regions in the galaxy by their colours. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}%%
\label{fig:ks,regs}
\end{figure}

@@

\begin{figure}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_tot2_f.png}
        \caption[Result from fitting the extended Schmidt law on the M31 data of the whole galaxy]{The result from fitting the extended Schmidt law on the surface density of SFR(FUV + 24~$\mu$m), the surface density of total gas and the surface density of stellar mass ($z$-axis) from the whole galaxy. Solid line shows the best fit (the mean value of the range reported in Table~\ref{table:res}) from a pixel-by-pixel method. Equivalent plots for the other SFR and gas tracers are in Fig.s~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} in the appendix.}
        \label{fig:es,all,fuv,tot}
    \end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/color_3d_fuv_tot.png}
\caption[Result from fitting the extended Schmidt law in three regions in M31]{Fitting result for SFR(FUV + 24~$\mu$m) vs total gas. Same as Fig.~\ref{fig:es,all,fuv,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}
\label{fig:es,regs,fuv,tot}
\end{figure}

@@

\subsection{The K-S Law in M31}

@@

\subsection{The Extended Schmidt Law in M31}
\label{sec:es_res}
The extended Schmidt law has been a recently proposed law \citep{Shi11}, which shows a tight correlation between the SFR and the total gas surface density and the surface density of the stellar mass. Our results from fitting the whole galaxy shows a sub-linear relation between \sigmasfr and \sigmastar.
Using only atomic gas, $\beta$ is in good agreement with the original suggestion of the extended Schmidt law, $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$. However, $\beta$ is much smaller in other two gas tracers. Using total gas mass, we find $\eqnprime$ to be very close to $\beta$. This relation suggests that, although increasing the total gas causes a decrease to the SFE, the existing stars will increase the SFE.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/metal_with_errors.png}
    \caption[The SFR(FUV + 24~$\mu$m) surface density and the stellar mass surface density versus gas/dust mass ratio]{Left: the SFR(FUV + 24~$\mu$m) surface density versus gas/dust mass ratio surface density and right: the stellar mass surface density versus gas/dust mass ratio surface density  shows the stellar mass. Each point shows a region with size of $\sim$750~pc. Typical uncertainties of the x-axes within 18~kpc are shown in upper right side of the plots. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}
    \label{fig:metal}
\end{figure}
